Semi-supervised author disambiguation of scientific publications

### 2015-07-16 paper.tex
autosave
added @eamonnmag

\author{Gilles Louppe\\
        CERN, Switzerland\\
        \texttt{g.louppe@cern.ch}\\
\And Hussein Al-Natsheh\\
        CERN, Switzerland\\
        \texttt{hussein.al.natsheh@cern.ch }\\
\And Mateusz Susik\\
        CERN, Switzerland\\
        \texttt{mateusz.susik@cern.ch }\\ }
\date{}

@@

Author name disambiguation in bibliographic databases is the problem of
grouping together scientific publications written by a same person. This
problem is often difficult because an author may use different spellings,
variants or synonyms across her career and/or distinct authors may share the
same name. Among solutions ot this problem, digital libraries are increasingly
offering tools for authors to manually curate their publications and claim
which ones are theirs. Indirectly, these tools allow for the inexpensive
collection of large annotated training data, which can be further leveraged to
build an automated disambiguation system capable of inferring features or
patterns for identifying publications written by a same person.  In this
context, we propose a semi-supervised machine learning disambiguation solution
in the case large and partially annotated databases of scientific publications.
Using a real-world dataset of 1 million manual annotations, we demonstrate how
to exploit this data (i) to learn an accurate classifier for identifying
corefering authors, (ii) to guide the clustering of scientific publications by
distinct authors in a semi-supervised way and finally (iii) to match the
resulting clusters with existing profiles.  Our analysis of parameters and
features reveal that... \glnote{To be completed with actual results.}

@@

In academic digital libraries, author name disambiguation is the problem of
grouping together publications written by a same person.  With the fast growth
of the scientific literature, this has become a pressing issue because the
accuracy of information managed at the individual level directly affects the
relevance search results (e.g., when querying for all publications written by a
given individual), the reliability of bibliometrics (e.g., citation counts or
other impact metrics) or the relevance of scientific network analysis. Author
name disambiguation is often a difficult problem because an author may use
different spellings, variants or synonyms across her career and/or distinct
authors may share the same name. In particular, author disambiguation becomes
even more critical for researchers from Eastern cultures, where personal names
may be traditionally less diverse (leading to homonym issues) or for which
transliteration to latin characters may not be unique (leading to synonym
issues).

Efforts and solutions to author disambiguation have been proposed in numerous
fields.

>>>>

\author{Gilles Louppe\\
        CERN\\
        Switzerland\\
\And Hussein Al-Natsheh\\
        CERN\\
        Switzerland\\
\And Mateusz Susik\\
        CERN\\
        Switzerland\\
\And Eamonn Maguire\\
        CERN\\
        Switzerland}
\date{}

@@

Author name disambiguation in bibliographic databases is the problem of
grouping together scientific publications written by a same person. This
problem is often difficult because an author may use different spellings,
variants or synonyms across her career and/or distinct authors may share the
same name. Among solutions ot this problem, digital libraries are increasingly
offering tools for authors to manually curate their publications and claim
which ones are theirs. Indirectly, these tools allow for the inexpensive
collection of large annotated training data, which can be further leveraged to
build an automated disambiguation system capable of inferring features or
patterns for identifying publications written by a same person.  In this
context, we propose a semi-supervised machine learning disambiguation solution
in the case large and partially annotated databases of scientific publications.
Using a real-world dataset of 1 million manual annotations, we demonstrate how
we exploited this data (i) to learn an accurate classifier for identifying
corefering authors, (ii) to guide the clustering of scientific publications by
distinct authors in a semi-supervised way and finally (iii) to match the
resulting clusters with existing profiles.  Our analysis of parameters and
features on this large training set reveal that... \glnote{To be completed with
actual results.}

@@

In academic digital libraries, author name disambiguation is the problem of
grouping together publications written by a same person.  With the fast growth
of the scientific literature, this has become a pressing issue because the
accuracy of information managed at the level of individuals directly affects
the relevance search results (e.g., when querying for all publications written
by a given author), the reliability of bibliometrics (e.g., citation counts or
other impact metrics) or the relevance of scientific network analysis. Author
name disambiguation is often a difficult problem because an author may use
different spellings, variants or synonyms across her career and/or distinct
authors may share the same name. In particular, author disambiguation becomes
even more critical for researchers from Eastern cultures, where personal names
may be traditionally less diverse (leading to homonym issues) or for which
transliteration to latin characters may not be unique (leading to synonym
issues).

Efforts and solutions to author disambiguation have been proposed from various
communities. On the one hand, libraries have maintained and developed
authorship control with manual curation
